Einlesen der Datensätze
```{r}

install_if_not <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  }
}

install_if_not("igraph")
edges <- read.csv("./data/edges.csv", header = TRUE)
nodes <- read.csv("./data/nodes.csv", header = TRUE)
```

installieren aller benötigten Pakete
```{r}
install_if_not("tidyverse")
install_if_not("dplyr")
install_if_not("GGally")
install_if_not("network")
install_if_not("tibble")
install_if_not("networkD3")
install_if_not("data.table")
install_if_not("ggplot2")

# Entfernen der Zeilen, welche eine ID enthalten, die nicht in den nodes steht
filteredEdges <- edges[edges$id_0 %in% nodes$spotify_id, ]
filteredEdges <- filteredEdges[filteredEdges$id_1 %in% nodes$spotify_id, ]
```
1. Forschungsfrage:
  Welche Genres sind am häufigsten in dem Datensatz enthalten
```{r}

numberOfGenres <- function(element) {
  element <- strsplit(element, ",")
  element <- unlist(element)
  return(length(element))
}

# Add column with genre of artist 0
filteredEdges["genre_0"] <- nodes[match(filteredEdges$id_0, nodes$spotify_id), "genres"]
# Add column with genre of artist 1
filteredEdges["genre_1"] <- nodes[match(filteredEdges$id_1, nodes$spotify_id), "genres"]


# transform the rows genre_0 and genre_1 into a vector
filteredEdges$genre_0 <- as.vector(filteredEdges$genre_0)
filteredEdges$genre_1 <- as.vector(filteredEdges$genre_1)

# create a new column with the genres of both artists
filteredEdges$genres <- paste(filteredEdges$genre_0, filteredEdges$genre_1, sep = ", ")

# remove the columns genre_0 and genre_1
filteredEdges <- filteredEdges[, -c(3, 4)]

#  count the genres
genreCounts <- table(unlist(strsplit(as.character(filteredEdges$genres), ", ")))
genreCounts <- as.data.frame(genreCounts)
colnames(genreCounts) <- c("genre", "count")
genreCounts <- genreCounts[order(genreCounts$count, decreasing = TRUE), ]

# remove [ and ] from the genres and replace no gonre with unknown
genreCounts$genre <- str_replace(genreCounts$genre, "\\[\\]", "unknown")
genreCounts$genre <- gsub("\\[", "", genreCounts$genre)
genreCounts$genre <- gsub("\\]", "", genreCounts$genre)


# plot the top 10 genres and safe plot to file
ggplot(genreCounts[1:10, ], aes(x = reorder(genre, count), y = count)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Genre", y = "Count of Collaborations", title = "Top 10 Genres in the Dataset")
ggsave("./visualizations/top10genres.png", width = 10, height = 5)


# calculate mean number of genres per artist
mean(unlist(lapply(filteredEdges$genres, numberOfGenres)))

# get count of nodes where genre == []
noGenre <- nodes %>%
  filter(genres == "[]") %>%
  count()

# count of nodes with genre like "pop dance" and "dance pop"
popDance <- nodes %>%
  filter(genres %like% "pop dance" & genres %like% "dance pop") %>%
  count()
```

3. Forschungsfrage:
  Korrelation der Follower von Artist 1 und Artist 2
```{r}
# create new dataframe with the spotify_ids of the artists
followerDataframe <- filteredEdges

# replace the spotify id by the number of followers
followerDataframe$id_0 <- nodes[match(followerDataframe$id_0, nodes$spotify_id), "followers"]
followerDataframe$id_1 <- nodes[match(followerDataframe$id_1, nodes$spotify_id), "followers"]

# rename the columns
colnames(followerDataframe) <- c("followers_0", "followers_1")

# calculate the correlation of the followers
cor(followerDataframe$followers_0, followerDataframe$followers_1, use = "complete.obs")
```

4. Forschungsfrage
  Kennzahlen der deutschen und der internationalen Szene im Vergleich
```{r}
# get 5 biggest artist
biggestArtists <- nodes %>%
  arrange(desc(followers)) %>%
  head(5)

# get five biggest german artists
biggestGermanArtists <- nodes %>%
  filter(genres %like% "deutsch" | genres %like% "german") %>%
  arrange(desc(followers)) %>%
  head(5)

# get the average followers of the biggest artists
mean(biggestArtists$followers)
mean(biggestGermanArtists$followers)

# get the count of collaborations of the biggest artists
biggestArtistsCollaborations <- filteredEdges %>%
  filter(id_0 %in% biggestArtists$spotify_id | id_1 %in% biggestArtists$spotify_id) %>%
  count()

# get the count of collaborations of the biggest german artists
biggestGermanArtistsCollaborations <- filteredEdges %>%
  filter(id_0 %in% biggestGermanArtists$spotify_id | id_1 %in% biggestGermanArtists$spotify_id) %>%
  count()

# get the count of genres of the biggest artists
biggestArtists$genres <- sapply(biggestArtists$genres, numberOfGenres)
mean(biggestArtists$genres)

# get the count of genres of the biggest german artists
biggestGermanArtists$genres <- sapply(biggestGermanArtists$genres, numberOfGenres)
mean(biggestGermanArtists$genres)

# get average popularity of the biggest artists
mean(biggestArtists$popularity)
mean(biggestGermanArtists$popularity)

#  correlation of popularity and followers
cor(nodes$popularity, nodes$followers, use = "complete.obs")
```

5. Forschungsfrage:
  Netzwerkplot international
```{r}
# get the 5 biggest artists
biggestArtists <- nodes[order(nodes$followers, decreasing = TRUE), ][1:5, ]


# get the collaborations of the 5 biggest artists
biggestArtistsCollaborationsEdges <- subset(filteredEdges, id_0 %in% biggestArtists$spotify_id | id_1 %in% biggestArtists$spotify_id)
rownames(biggestArtistsCollaborationsEdges) <- NULL
# rename id_0 to source and id_1 to target
colnames(biggestArtistsCollaborationsEdges) <- c("source", "target")

# filter nodes if they are not in biggestArtistsCollaborations
biggestArtistsNodes <- nodes[nodes$spotify_id %in% biggestArtistsCollaborationsEdges$source | nodes$spotify_id %in% biggestArtistsCollaborationsEdges$target, ]

# replace the id by a number
biggestArtistsNodes$new_id <- as.numeric(factor(biggestArtistsNodes$spotify_id))

#  replace each id in biggestArtistsCollaborations with the new_id
biggestArtistsCollaborationsEdges$source <- biggestArtistsNodes[match(biggestArtistsCollaborationsEdges$source, biggestArtistsNodes$spotify_id), "new_id"]
biggestArtistsCollaborationsEdges$target <- biggestArtistsNodes[match(biggestArtistsCollaborationsEdges$target, biggestArtistsNodes$spotify_id), "new_id"]

# print row where spotify_id is '215', '253'
biggestArtistsNodes[biggestArtistsNodes$new_id %in% c(215, 253), ]

# somehow "Armaan Malik" and "SLAVA MARLOW" are twice in the dataset -> remove one of them
biggestArtistsNodes <- subset(biggestArtistsNodes, !(new_id == 215 & name == "Armaan Malik" & followers == 5))
biggestArtistsNodes <- subset(biggestArtistsNodes, !(new_id == 253 & name == "SLAVA MARLOW" & followers == 347))

# order the nodes by spotify_id
biggestArtistsNodes <- biggestArtistsNodes[order(biggestArtistsNodes$spotify_id), ]

# set spotify_id as rownames
rownames(biggestArtistsNodes) <- biggestArtistsNodes$new_id

# add column with true or false if artist in biggestArtists to biggestArtistsNodes
biggestArtistsNodes <- cbind(biggestArtistsNodes, isBiggestArtist = biggestArtistsNodes$spotify_id %in% biggestArtists$spotify_id)

# drop spotify_id column
biggestArtistsNodes <- biggestArtistsNodes[, -1]

# change the wording of isbiggestArtist to "TOP 5" or "OTHER"
biggestArtistsNodes$isBiggestArtist <- ifelse(biggestArtistsNodes$isBiggestArtist == TRUE, "TOP 5", "OTHER")

# lower source and target by 1
biggestArtistsCollaborationsEdges$source <- biggestArtistsCollaborationsEdges$source - 1
biggestArtistsCollaborationsEdges$target <- biggestArtistsCollaborationsEdges$target - 1

d <- forceNetwork(
  Links = biggestArtistsCollaborationsEdges,
  Nodes = biggestArtistsNodes,
  Source = "source",
  Target = "target",
  NodeID = "name",
  Group = "isBiggestArtist",
  opacity = 0.8,
  fontSize = 20,
  Nodesize = "followers",
  radiusCalculation = JS("(d.nodesize / 10000000)+5"),
  zoom = TRUE,
  colourScale = JS("d3.scaleOrdinal([ '#05f2fa','#021433'])"),
  legend = TRUE,
)

saveNetwork(d, file = "./visualizations/biggestArtistsCollaborations.html")
  ```

2. Forschungsfrage:
  Welche Genres besitzen die größte Reichweite?
```{r}
# get a list of all genres
genres <- unlist(strsplit(nodes$genres, ","))
# remove empty strings, remove whitespaces, [ and ], and ' from the strings
genres <- gsub("\\[", "", genres)
genres <- gsub("\\]", "", genres)
genres <- gsub("'", "", genres)
# remove empty strings
genres <- genres[genres != ""]
# get the unique genres

# cut leading and tailing whitespaces
genres <- gsub("^\\s+|\\s+$", "", genres)

#  delete empty strings
genres <- genres[genres != ""]

genres <- unique(genres)
length(genres)

# create a dataframe with the genres and the number of followers
genresFollowers <- data.frame(genre = genres, followers = 0)

# get duplicates
duplicates <- duplicated(genresFollowers$genre)



# create function to get the number of followers for a genre
getFollowers <- function(genre) {
  return(sum(nodes[nodes$genres %like% genre, ]$followers))
}


# for each genre, add the followers of the artists that have this genre
genresFollowers$followers <- sapply(genresFollowers$genre, getFollowers)


# sort the genres by the number of followers
genresFollowers <- genresFollowers[order(genresFollowers$followers, decreasing = TRUE), ]

# drop duplicated genres
genresFollowers <- genresFollowers[!duplicated(genresFollowers$genre), ]


library(scales)
# plot top 10 genres and safe
topFollowed <- ggplot(genresFollowers[1:10, ], aes(x = reorder(genre, followers, decreasing = TRUE), y = followers)) +
  geom_bar(stat = "identity") +
  labs(x = "Genre", y = "Number of followers") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_discrete(labels = scales::comma)
ggsave("./visualizations/topFollowed.png", topFollowed)

# plot top 10 genres and safe
topFollowed <- ggplot(genresFollowers[1:10, ], aes(x = reorder(genre, followers, decreasing = TRUE), y = followers)) +
  geom_bar(stat = "identity") +
  labs(x = "Genre", y = "Number of followers") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_discrete(labels = scales::comma)
ggsave("./visualizations/topFollowed.png", topFollowed)



# function to get average followers for a genre
getAvgFollowers <- function(genre) {
  return(mean(nodes[nodes$genres %like% genre, ]$followers))
}

# create a dataframe with the genres and the average number of followers
genresAvgFollowers <- data.frame(genre = genres, avgFollowers = 0)

# for each genre, add the average followers of the artists that have this genre
genresAvgFollowers$avgFollowers <- sapply(genresAvgFollowers$genre, getAvgFollowers)

# sort the genres by the average number of followers
genresAvgFollowers <- genresAvgFollowers[order(genresAvgFollowers$avgFollowers, decreasing = TRUE), ]

# plot the genres with the most average followers and safe it as a png
barplot(genresAvgFollowers$avgFollowers, names.arg = genresAvgFollowers$genre, las = 2, cex.names = 0.5, col = "blue")
dev.copy(png, file = "genresAvgFollowers.png")
dev.off()

# save the dataframes as csv
write.csv(genresFollowers, file = "genresFollowers.csv")
write.csv(genresAvgFollowers, file = "genresAvgFollowers.csv")
```

5. Forschungsfrage
  Plot der deutschen Musikszene
```{r}
#  get all german artists in rap
germanArtistsNodes <- nodes[nodes$genre %like% "german" | nodes$genre %like% "deutsch", ]
# get the 5 biggest artists
germanArtistsNodes <- germanArtistsNodes[order(germanArtistsNodes$followers, decreasing = TRUE), ][1:5, ]


# get the collaborations of the 5 biggest artists
germanArtistsEdges <- subset(filteredEdges, id_0 %in% germanArtistsNodes$spotify_id | id_1 %in% germanArtistsNodes$spotify_id)
rownames(germanArtistsEdges) <- NULL
# rename id_0 to source and id_1 to target
colnames(germanArtistsEdges) <- c("source", "target")

# filter nodes if they are not in biggestArtistsCollaborations
germanArtistsNodes <- nodes[nodes$spotify_id %in% germanArtistsEdges$source | nodes$spotify_id %in% germanArtistsEdges$target, ]

# replace the id by a number
germanArtistsNodes$new_id <- as.numeric(factor(germanArtistsNodes$spotify_id))

#  replace each id
germanArtistsEdges$source <- germanArtistsNodes[match(germanArtistsEdges$source, germanArtistsNodes$spotify_id), "new_id"]
germanArtistsEdges$target <- germanArtistsNodes[match(germanArtistsEdges$target, germanArtistsNodes$spotify_id), "new_id"]

# order by new_id
germanArtistsNodes <- germanArtistsNodes[order(germanArtistsNodes$new_id), ]

# set spotify_id as rownames
rownames(germanArtistsNodes) <- germanArtistsNodes$new_id


# drop spotify_id column
germanArtistsNodes <- germanArtistsNodes[, -1]

# insert row isgerman
germanArtistsNodes$isgerman <- germanArtistsNodes$genre %like% "german" | germanArtistsNodes$genre %like% "deutsch"

# change wording of isgerman to "deutsch" and "nicht deutsch"
germanArtistsNodes$isgerman <- ifelse(germanArtistsNodes$isgerman, "deutsch", "nicht deutsch")

# lower source and target by 1
germanArtistsEdges$source <- germanArtistsEdges$source - 1
germanArtistsEdges$target <- germanArtistsEdges$target - 1

n <- forceNetwork(
  Links = germanArtistsEdges,
  Nodes = germanArtistsNodes,
  Source = "source",
  Target = "target",
  NodeID = "name",
  Group = "isgerman",
  opacity = 0.8,
  fontSize = 20,
  Nodesize = "followers",
  radiusCalculation = JS("(d.nodesize / 10000000)+5"),
  zoom = TRUE,
  colourScale = JS("d3.scaleOrdinal([ '#05f2fa','#021433'])"),
  legend = TRUE,
)

saveNetwork(n, file = "./visualizations/germanMusicScene.html")
```


5. Forschungsfrage
  Plot der deutschen Musikszene (top 5 Populär - nicht meisten follower)
```{r}
#  get all german artists in rap
germanArtistsNodes <- nodes[nodes$genre %like% "german" | nodes$genre %like% "deutsch", ]
# get the 5 biggest artists
germanArtistsNodes <- germanArtistsNodes[order(germanArtistsNodes$popularity, decreasing = TRUE), ][1:5, ]


# get the collaborations of the 5 biggest artists
germanArtistsEdges <- subset(filteredEdges, id_0 %in% germanArtistsNodes$spotify_id | id_1 %in% germanArtistsNodes$spotify_id)
rownames(germanArtistsEdges) <- NULL
# rename id_0 to source and id_1 to target
colnames(germanArtistsEdges) <- c("source", "target")

# filter nodes if they are not in biggestArtistsCollaborations
germanArtistsNodes <- nodes[nodes$spotify_id %in% germanArtistsEdges$source | nodes$spotify_id %in% germanArtistsEdges$target, ]

# replace the id by a number
germanArtistsNodes$new_id <- as.numeric(factor(germanArtistsNodes$spotify_id))

#  replace each id
germanArtistsEdges$source <- germanArtistsNodes[match(germanArtistsEdges$source, germanArtistsNodes$spotify_id), "new_id"]
germanArtistsEdges$target <- germanArtistsNodes[match(germanArtistsEdges$target, germanArtistsNodes$spotify_id), "new_id"]

# order by new_id
germanArtistsNodes <- germanArtistsNodes[order(germanArtistsNodes$new_id), ]

# set spotify_id as rownames
rownames(germanArtistsNodes) <- germanArtistsNodes$new_id


# drop spotify_id column
germanArtistsNodes <- germanArtistsNodes[, -1]

# insert row isgerman
germanArtistsNodes$isgerman <- germanArtistsNodes$genre %like% "german" | germanArtistsNodes$genre %like% "deutsch"

# change wording of isgerman to "deutsch" and "nicht deutsch"
germanArtistsNodes$isgerman <- ifelse(germanArtistsNodes$isgerman, "deutsch", "nicht deutsch")

# lower source and target by 1
germanArtistsEdges$source <- germanArtistsEdges$source - 1
germanArtistsEdges$target <- germanArtistsEdges$target - 1

n <- forceNetwork(
  Links = germanArtistsEdges,
  Nodes = germanArtistsNodes,
  Source = "source",
  Target = "target",
  NodeID = "name",
  Group = "isgerman",
  opacity = 0.8,
  fontSize = 20,
  Nodesize = "followers",
  radiusCalculation = JS("(d.nodesize / 10000000)+5"),
  zoom = TRUE,
  colourScale = JS("d3.scaleOrdinal([ '#05f2fa','#021433'])"),
  legend = TRUE,
)

saveNetwork(n, file = "./visualizations/germanMusicSceneBasedOnPopularity.html")
```

